---
title: "Weight of Fish"
author: "Adriana Pimentel"
date: "Year 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
mydata <- read.csv(file="Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
pike <- filter(mydata, Species =="Pike")
pike <- select (pike, -Species)
roach <- filter(mydata, Species =="Roach")
roach <- select(roach, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
After running the data and choosing the perch data to look at, we figured out that we need to upload the Numerical~Numerical helper file.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(Weight~Height,data=perch)
basicNN <- ggplot(perch,aes(y=Weight,x=Height))
basicNN + geom_point()
plot(Weight~Width, data=perch)
basicNN <- ggplot(perch,aes(y=Weight,x=Width))
basicNN + geom_point()
```

Each plot shows an increasing correlation. In the first plot, the relationship between Height and Weight has an increasing correlation as well as the plot with Width and Weight. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
cor(Weight~Height,data=perch)
```

The correlation between Height and Weight is about 1.0. 

```{r}
cor(Weight~Width,data=perch)
```
The correlation between Weight and Width is about 1.0. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
model.1 <- lm(Weight~Height,data=perch)
summary.lm(model.1)
```
```{r}
model.1 <- lm(Weight~Width,data=perch)
summary.lm(model.1)
```

Height and Width are both good variables to compare weight to as the Adjusted R-squared is around .9. The equation for the fist inferential test is Weight=116.965*Height-537.328.
The equation for the second inferential test is Weight= 188.819*Width-513.845.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In this problem we first filtered out the Species data because it was not needed in this problem and then we select the perch data out of mydata. Then we figured out what helper file we need to use which was a numerical~numerical.rmd file according to the data given. Then we ran numerical and inferential results to predict the weight of perch. We figured out that weight increases as Width and Height increases. 